Clean 2015 Raw Data

### 2017-08-25 data-raw/01-Clean_2015_Raw_Data.Rmd
Update 01-Clean_2015_Raw_Data.Rmd

`load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))`
`load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))`
`load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))`
`load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))`

>>>>

The raw data are located in the `extdata` folder of the installed
_rice.awd.pests_ and can be accessed using:
```r
load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))
```
